|

### 2020-05-19 paper/Manuscript.Rmd
finish writing FAIR

The functionality of 'Git' is amplified by services such as 'GitHub'
(https://github.com. 'GitHub' is best understood as a cloud
storage service with social networking functionality. The cloud storage aspect
of 'GitHub' works as follows: You can "clone" (copy) a local 'Git' repository to
the 'GitHub' website, as a backup or research archive. The social network aspect
comes into play when a repository on 'GitHub' is set to "public": This allows 
other researchers to peruse the repository and see how the work was done, clone
it to their own computer to replicate the original work or apply the methods to
their own data, open "Issues" to ask questions or give feedback on the project,
or even send a "Pull request" with suggested changes to the text or code for
your consideration. 'Git' and 'GitHub' shine as tools for collaboration, because
different people can simultaneously work on different parts of a project, and
their changes can be compared and automatically merged on the website. Even on
solo projects, working with 'Git'/'GitHub' has many benefits: Staying organized,
being able to start a new study with a clone of an old, similar repository, or
splitting off an "experimental branch" to try something new, while retaining the
ability to "revert" (return) to a previous state of the project, or to "merge"
(incorporate) the experimental branch. Although this paper focuses on 'GitHub',
`worcs` (as of version 0.1.2) supports alternative services such as 'GitLab'
(https://gitlab.com) and 'Bitbucket' (https://bitbucket.org), and has a vignette
detailing instructions for these platforms.

@@

>>>>

The functionality of 'Git' is amplified by services such as 'GitHub'
(https://github.com). 'GitHub' is best understood as a cloud storage service
with social networking functionality. The cloud storage aspect
of 'GitHub' works as follows: You can "clone" (copy) a local 'Git' repository to
the 'GitHub' website, as a backup or research archive. The social network aspect
comes into play when a repository on 'GitHub' is set to "public": This allows 
other researchers to peruse the repository and see how the work was done, clone
it to their own computer to replicate the original work or apply the methods to
their own data, open "Issues" to ask questions or give feedback on the project,
or even send a "Pull request" with suggested changes to the text or code for
your consideration. 'Git' and 'GitHub' shine as tools for collaboration, because
different people can simultaneously work on different parts of a project, and
their changes can be compared and automatically merged on the website. Even on
solo projects, working with 'Git'/'GitHub' has many benefits: Staying organized,
being able to start a new study with a clone of an old, similar repository, or
splitting off an "experimental branch" to try something new, while retaining the
ability to "revert" (return) to a previous state of the project, or to "merge"
(incorporate) the experimental branch. This paper focuses on 'GitHub', which is
the most widely used 'Git' cloud storage services. However, as of version 0.1.2,
`worcs` projects can interchangeably use the two main alternative services,
'GitLab' (https://gitlab.com) and 'Bitbucket' (https://bitbucket.org). The
package has a [vignette]() with additional instructions for using these platforms.

@@

WORCS encourages and simplifies the adoption of Open Science principles in daily scientific work. It helps researchers make all research output created throughout the scientific process - not just manuscripts, but data, code, and methods - open and publicly assessible. This enables other researchers to reproduce results, facilitates cumulative science by allowing others to make direct use of these research objects.

Sharing all research output also provides a proper basis for research evaluation according to the San Francisco Declaration on Research Assessment (DORA; https://sfdora.org/), which increasingly plays a role in grant funding and hiring or promotion procedures. Direct access to research objects allows funding bodies and hiring committies to evaluate research quality based on content rather than relying on spurious surrogate indicators like journal impact factors, conference rankings, and h-indexes. The detailed version control and commit tracking of github and similar platforms furthermore make it possible to assess the relative contributions made by different researchers.

The FAIR Guiding Principles for scientific data management and stewardship [@wilkinsonFAIRGuidingPrinciples2016a] advocate that research data should be 
Findable, Accessible, Interoperable and Reusable. Moreover, these principles are
increasingly applied to other types of research output 
[@lamprechtFAIRPrinciplesResearch2019]. Research
organizations and funders use the FAIR principles as standard for open, 
transparent and reproducible science.
The WORCS workflow helps users meet the FAIR principles by making all research objects -
including (origina) data and code - accessible in a (public) repository. 
The `worcs` package additionally
facilitates meeting the FAIR principles in several ways. First, each `worcs` project has a YAML file
(https://yaml.org/) that lists the research objects in the project, which will allow web crawlers 
to index `worcs` projects. Second, a codebook is automatically generated for each data file stored
using `open_data()` or `closed_data()`. We encourage users to elaborate on the default codebook by adding
variable description and categories, which might - in the future - enable indexing data by topic area. 
Relatedly, `worcs` is itself an example of FAIR research software [see @lamprechtFAIRPrinciplesResearch2019 and https://fair-software.eu/]. It is hosted on a public version controlled repository ('GitHub'), it has an open source licence (GPL v3.0), is registered in a community registry (CRAN), it enables the citation of the software (using the `citation("worcs")` command, or by citing this paper), and followed the CII Best Practices software quality checklist during development.
